Informative Autonomous Sampling of Oceanographic Variables Using Joint Excursion Sets

### 2019-10-17 main_new.tex
Update

  Improving and optimizing oceanographic sampling is a crucial task for marine science and maritime management. Faced with limited resources to understand processes in the water-column, the combination of statistics and autonomous robotics provides new opportunities for experimental designs. In this work we develop methods for efficient spatial sampling applied to the mapping of coastal processes by providing informative descriptions of spatial characteristics of ocean phenomena. Specifically, we define a design criterion based on reducing uncertainty in the joint excursions of vector-valued Gaussian random fields, and derive tractable expressions for the expected Bernoulli variance reduction in such a framework. We demonstrate how this criterion gives a description of the boundary uncertainty in temperature and salinity variables, which is used to prioritize sampling efforts at locations that are ambiguous, making exploration more effective by building on myopic and non-myopic strategies. We use simulations to study the properties of methods and to compare them with state-of-the-art approaches, followed by results from field deployments with an autonomous underwater vehicle as part of a case study mapping the boundary of a river plume. The results demonstrate the potential of combining statistical methods and robotic platforms to effectively inform and execute data-driven environmental sampling.

@@

\item With limited available information about the state of the ocean, there is substantial value in reacting to
  information obtained from measurements taken in-situ. This
  acquired information must be assimilated into statistical models that
  can be used to inform decisions on where to sample
  sequentially.%\emph{in-situ}; this is usually referred to as the \emph{adaptivity gap} \citep{Krause2008phd}.

@@

The covariance is assumed to be stationary and separable for the two variables. 
The $2 \times 2$ pointwise covariance matrix is set to:
\begin{equation}\label{v0}
\bSigma(\bx)=\mbox{Var} 
\begin{bmatrix}
    \xi_T(\bx) \\
    \xi_S(\bx) 
    \end{bmatrix}=
\begin{bmatrix}
0.25^2 & 0.6 \cdot 0.25^2 \\
0.6 \cdot 0.25^2 & 0.25^2
\end{bmatrix}.
\end{equation}
The spatial correlation is of a Matern type \kc{cite or define}:
\begin{equation}\label{v}
\small
\mbox{Corr} 
\left(
\begin{bmatrix}
    \xi_T(\bx) \\
    \xi_S(\bx) 
    \end{bmatrix},
    \begin{bmatrix}
    \xi_T(\bx') \\
    \xi_S(\bx') 
    \end{bmatrix}
    \right)
    = \begin{bmatrix}
1 & 0.6  \\
0.6  & 1
\end{bmatrix}(1+\phi h)\exp (-\phi h),
\end{equation}
where $h=\sqrt{||\bx-\bx'||^2}$ and $\phi=0.3$ indicates an effective correlation range of about $1200$ m. 
%Figure \ref{fig:stat_design} shows the contour lines for the EP for the reference. We notice the trend of increasing salinity and temperature to the west.  
One realization of the random fields representing salinity and
temperature is shown in Fig. \ref{fig:true_temp} and
\ref{fig:true_sal}. The true ES is a realization from this model as shown
in Fig. \ref{fig:ESet}.

>>>>

  Improving and optimizing oceanographic sampling is a crucial task for marine science and maritime management. Faced with limited resources to understand processes in the water-column, the combination of statistics and autonomous robotics provides new opportunities for experimental designs. In this work we develop methods for efficient spatial sampling applied to the mapping of coastal processes by providing informative descriptions of spatial characteristics of ocean phenomena. Specifically, we define a design criterion based on reducing uncertainty in the joint excursions of vector-valued Gaussian random fields, and derive tractable expressions for the expected Bernoulli variance reduction in such a framework. We demonstrate how this criterion gives a description of the boundary uncertainty, that can be used to prioritize sampling efforts at locations that are ambiguous, making exploration more effective. We use simulations to study the properties of methods and to compare them with state-of-the-art approaches, followed by results from field deployments with an autonomous underwater vehicle as part of a case study mapping the boundary of a river plume. The results demonstrate the potential of combining statistical methods and robotic platforms to effectively inform and execute data-driven environmental sampling.

@@

\item With limited available information about the state of the ocean, there is substantial value in reacting to
  information obtained from measurements taken in-situ. This
  acquired information must be assimilated into statistical models that
  can be used to inform decisions on where to sample
  sequentially.%\emph{in-situ}; this is usually referred to as the \emph{adaptivity gap} \citep{ause2008phd}.

@@

The covariance is assumed to be stationary and separable for the two variables. 
The $2 \times 2$ pointwise covariance matrix is set to:
\begin{equation}\label{v0}
\bSigma(\bx)=\mbox{Var} 
\begin{bmatrix}
    \xi_T(\bx) \\
    \xi_S(\bx) 
    \end{bmatrix}=
\begin{bmatrix}
0.25^2 & 0.6 \cdot 0.25^2 \\
0.6 \cdot 0.25^2 & 0.25^2
\end{bmatrix}.
\end{equation}
The spatial correlation is of a Matern type \citep{Matern2013}:
\begin{equation}\label{v}
\small
\mbox{Corr} 
\left(
\begin{bmatrix}
    \xi_T(\bx) \\
    \xi_S(\bx) 
    \end{bmatrix},
    \begin{bmatrix}
    \xi_T(\bx') \\
    \xi_S(\bx') 
    \end{bmatrix}
    \right)
    = \begin{bmatrix}
1 & 0.6  \\
0.6  & 1
\end{bmatrix}(1+\phi h)\exp (-\phi h),
\end{equation}
where $h=\sqrt{||\bx-\bx'||^2}$ and $\phi=0.3$ indicates an effective correlation range of about $1200$ m. 
%Figure \ref{fig:stat_design} shows the contour lines for the EP for the reference. We notice the trend of increasing salinity and temperature to the west.  
One realization of the random fields representing salinity and
temperature is shown in Fig. \ref{fig:true_temp} and
\ref{fig:true_sal}. The true ES is a realization from this model as shown
in Fig. \ref{fig:ESet}.
